---
title: "Untitled"
output: html_document
---




### Question 1:

Using a loop, print the integers from 1 to 50. 
```{r}
v <- c(1:50)
for (i in 1:length(v)) {print(v[i])}

```

### Question 2:

A.  Using a loop, add all the integers between 0 and 1000.
```{r}
v1 <- c(0:1000)
a = 0
for (i in 1:length(v1)) {a= a + v1[i]}
print(a)
```

B. Now, add all the EVEN integers between 0 and 1000 (hint: use seq())
```{r}
v2 <- seq(0,1000, by=2)
c=0
for (i in 1:length(v2)) {c = c + v2[i]} 
print(c)

```

C. Now, repeat A and B WITHOUT using a loop.
```{r}
#A:
sum(0:1000)

#B:
sum(seq(0,1000,by=2))

```
### Question 3:

Here is a dataframe of survey data containing 5 questions :

```{r, eval=FALSE}
survey <- data.frame(
                     "participant" = c(1, 2, 3, 4, 5, 6),
                     "q1" = c(5, 3, 2, 7, 11, 0),
                     "q2" = c(4, 2, 2, 5, -10, 99),
                     "q3" = c(-4, -3, 4, 2, 9, 10),
                     "q4" = c(-30, 5, 2, 23, 4, 2),
                     "q5" = c(88, 4, -20, 2, 4, 2)
                     )
survey
```
The response to each question should be an integer between 1 and 5. Obviously, we have some bad values in the dataframe. The goal of this problem is to fix them.

A. Using a loop, create a new dataframe called survey.clean where all the invalid values (those that are not integers between 1 and 5) are set to NA.
```{r}
for (i in 1:nrow(survey)) {
  for (j in 2:ncol(survey)) {
    if (survey[i,j]<1 | survey[i,j]>5)
    survey[i,j]=NA
  }
}
survey.clean = survey
survey.clean

```
B. Now, again using a loop, add a new column to the dataframe called ¡°invalid.answers¡± that indicates, for each participant, how many bad answers they gave.
```{r}
for (i in 1:nrow(survey.clean)) {
     survey.clean$invalid.answer[i] = sum(is.na(survey.clean[i,]))}
survey.clean

```
